ECCCos from the Black Box:\\ Faithful Explanations through\\ Energy-Constrained Conformal Counterfactuals

### 2023-09-26 paper/appendix.tex
done

>>>>

In our experiments we always generate multiple counterfactuals for each model and generator. Each time the factual and target class is drawn randomly. For each generator and model we choose $n_f=100$ factuals for all of our synthetic and vision data. For tabular data we choose $n_f=25$ because larger values made grid search computationally prohibitive. For vision data, grid search was computationally prohibitve in any case, so hyperparameters were tuned manually. For all other datasets grid search was performed over different combinations of penalty strengths and optimizer steps sizes.
